Highlighting Disputed Claims on the Web

### 2009-10-29 papers/www_disputefinder/disputefinder.tex
Applied Beth changes and puled most of the related work content into the body of the paper

The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}. If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information.

@@

In the realm of News, Pew~\cite{pew-news} reports that, while Internet news is rapidly gaining ground on traditional news sources, most online news sources are not considered credible. Even when users are getting news from the websites of traditional news providers, it is likely that they read news from a variety of unfamiliar news sources~\cite{pew-news}, rather than the small set of newspapers and TV stations that they might have followed in the past.

@@

@@

Dispute Finder consists of a database, an API, and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}). The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claims. The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims. The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.

\todo{Figure that does a smaller highlight}

There are several design decisions that must be made when building a system such as this. In particular:

\begin{description}
\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large (so a user is likely to see snippets highlighted reasonably often) and accurate (so users are not distracted by things that they would not consider to be disputed). We currently use a combination of crowd-sourcing from users, and mining web sites such as Snopes and Politifact that already maintain lists of disputed claims. More generally, the challenge is not to determine if a claim is disputed by {\it anyone} but to determine whether there is an alternative point of view that this particular user would take seriously.

\item[How do we find disputed snippets?] Given a particular web page, how do we determine which phrases on that page are making known disputed claims? We have experimented with several different approaches, each of which has different advantages and disadvantages. One can ask users to mark snippets individually. One can build a search tool that allows a user to find and mark similar snippets in bulk. One can provide an interface that allows a user to train a machine learning classifier to recognize snippets. One can run a textual entailment algorithm on the client that looks for phrases that look similar to a known claim.

\item[How do we highlight snippets?] How do we tell what web page a user is reading, and augment their interface to alert them about disputed claims? Using a browser extension allows us to examine all content the user browses, but limits us to users who are prepared to install a browser extension. Using a proxy~\cite{Barrett1997} has similar adoption problems to a browser extension, and is likely to break some web sites. If external sites such as news readers and search engines use our API then they can provide information about disputed claims to users without them having to install anything, but this limits coverage to content accessed through sites that use the API.

\item[How should we explain a disputed claim?] If someone requests more information about a disputed claim by clicking on a highlighted snippet, what information should we show them that will help them decide whether to consider alternative points of view? We tried an argumentation graph and lists of articles that support or oppose the claim.
\end{description}

If users are going to adopt Dispute Finder, it is important that it provides users with a service that they feel will be of benefit to them, and has an interface that they can use. Dispute Finder is designed to cater to two personas. Each persona was created from interviews we conducted with people who we believe fit into these categories.

@@

We used several different methods to gain input from users. We performed three rounds of users studies, circulated a survey within a target group, and conducted a series of interviews. We discuss the conclusions of these studies throughout the paper, and in a section at the end. These studies were intended to inform the design of Dispute Finder, rather than to validate it. The only way to conclusively demonstrate that Dispute Finder is useful would be for it to be adopted by many active users -- something that the current implementation is not mature enough to support.

\todo{Improve the paraphraser UI so it shows users what pages are making the claim}
\todo{Improve the ``see examples on the web'' UI to it shows the pages that were found with the activists training work}
\todo{Provide a customized RSS reader and search engine that does dispute tracking. - future work?}

\todo{Should we explicitly list what we think are our key contributions?}

%\section{Related Work}
%
%Dispute Finder builds on prior work in many different areas. The idea of highlighting potentially untrustworthy information was applied to Wikipedia by WikiTrust~\cite{Adler2008a}. Tagging Systems~\cite{Marlow2006} influenced the way Dispute Finder uses the community to collect and filter information. Dispute Finder's snippets are influenced by clipping tools such as Internet Scrapbook~\cite{Sugiura1998}. Many people have developed textual entailment algorithms~\cite{entail?} that determine when one sentence implies the trust of another, or contradiction detection algorithms that determine when one sentence contradicts another.
%
%\todo{Add more references from the NewsCube paper}

%
%\subsection{Finding Disputed Information on the Web}
%
%An important part of Dispute Finder is identifying what claims are disputed. Several other authors looked at disputed information on the web.
%
%Kittur et al~\cite{Kittur2007} developed an algorithm that can determine whether a wikipedia page is about a disputed topic. Kittur and Chi~\cite{Kittur2009} broke down the disputed pages by catagory and found that People, Society, and Religion were the categories with the most disputed pages.
%
%\subsection{Extracting Information from the Web}
%
%Information extration tools such as TextRunner~\cite{Etzioni2008} 
%Read The Web
%
%TextRunner~\cite{Etzioni2008} 
%
%\todo{cite lots of Etzioni stuff}
%
%\cite{SnowBall}
%\cite{Read The Web}
%\cite{Information Extraction from Wikipedia}
%\cite{KnowItAll}
%\cite{TextRunner}
%
%\todo{Online Dispute Resolution}
%
%\todo{Cite Kittur et al}

\subsection{Augmented Web Navigation}

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in.

%\subsection{Persuasive Technology}

% \subsection{Semantic Web}
% 
% Nobody is going to mark up their own web page as being wrong.

% \subsection{To discuss in the body}
% 
% Paraphrases~\cite{Chklovski2005}. Suggested formal paraphrases~\cite{Blythe2004}.
% Importance of Lurkers~\cite{Takahashi2003}
% Wikify~\cite{Mihalcea2007}. OpenCalais\footnote{http://opencalais.com}.

@@

\subsection{Measuring Trust}

Several authors have analyzed trust on Wikipedia. WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author. Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest. All these tools determine trustworthiness by examining the edit history of a page.

BJ Fogg et al~\cite{Fogg2000, Fogg2003} have looked at the metrics that users use to determine when they should trust a source online. They found that the most important factor was whether a web site had a professional-looking design. Gill and Arts~\cite{Gil2006} identified on a different set of factors, including topic (a medical site may not be trusted on car repair), popularity and authority.

\todo{Talk about how this information was used in the design of Dispute Finder.}

\subsection{Fact Checking Sites}

If a user suspects that something they read online may be false then they can look it up on one of many fact checking sites such as Snopes.com, FactCheck.org, or Politifact.com. If one is aware that an issue is controversial and wants to understand the different sides, then one can use sites like Wikipedia.org, Debate.org, and ProCon.org. These sites do an excellent job presenting accurate and balanced information about controversial topics.

@@

\subsection{Analyzing News}

While Dispute Finder is not intended to be applied only to news content, News is a particularly interesting source of disputed information, and one that others have looked at before.

News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story. The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue. Dispute Finder is trying to do something similar, but working at the finer granularity of specific claims made in an article, rather than the overall slant of the article. A reader may not have the patience to read multiple articles about the same topic, or may not find the article that rebuts the claim made in an article they read.

Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias. Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking. Newstrust allows users to rate news articles for quality and objectivity.

\section{What is Disputed?}

One of the biggest challenges in Dispute Finder, is how to build a list of disputed claims that should be highlighted for users. As discussed in Section~\ref{related:entailment}, rather than directly inferring whether a snippet is disputed by a trusted article on the web, Dispute Finder instead builds a database of known disputed claims and tries to determine whether a snippet on a web page entails the truth of one of these claims.

\todo{We are repeating information between here and the related work section on Recognizing Textual Entailment}

We do not want the database of disputed claims to contain everything that has ever been disputed by anyone. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence that the moon is made of cheese, but few people believe this claim is true. What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.

@@

Fortunately, several web sites already maintain databases of disputed claims, together with arguments against them. For example Snopes.com maintains a list of urban legends and Politifact.com maintains a list of false claims about politics. We automatically import all claims that from these sites into our database. In the future we intend to also import claims from other such sites, and allow users to choose which feeds of disputed claims should be used to highlight snippets on pages they browse.

@@

\todo{Say how many disputed claims}

\todo{talk about duplicates}

\todo{Actually import the Politifact data}

@@

Given a web page, Dispute Finder needs to identify which snippets are making known disputed claims. We implemented and tested four different approaches:

@@

Explicit page marking has the highest accuracy, but the poorest coverage. Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. We also found that it can also be hard to motivate a user to mark snippets if it is unlikely that another user with the Dispute Finder extension will read exactly this page. This same problem that has hindered the adoption of numerous web page annotation tools.

@@

Client side entailment gets even more coverage. Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined. This is particularly important for news pages, which are frequently read only a few minutes after they have been written. Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and information on an intranet.

@@

The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm that is a common baseline in NLP. It divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

@@

\subsection{Sensemaking and Argumentation Tools}

\todo{Talk about this work in the introduction?}

Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users. TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph. ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document. Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it.

Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''. An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.

\subsection{Recognizing Textual Entailment}
\label{related:entailment}

\todo{Trim this down??}

The textual entailment problem is one of the standard problems in natural language processing. In the 3-way variant of the PASCAL Recognizing Textual Entailment (RTE) Challenge\footnote{http://pascallin.ecs.soton.ac.uk/Challenges/RTE/}, an algorithm is given two sentences T and H and asked to return one of three answers: T {\it entails} H, T {\it contradicts} H, or the truth of H cannot be determined from T.

Several of the core challenges in Dispute Finder are forms of the textual entailment problem. Finding disputed claims is a special case of finding two sentences on the web, such that one {\it contradicts} the other. Finding a snippet that makes a disputed claim is a special case of finding a snippet that {\it entails} a disputed claim.

One could in theory determine which snippets to highlight by using a textual entailment algorithm to determine whether any snippet is {\it contradicted} by any other sentence on the web, however the vast number of sentences that one would have to compare makes this approach impractical. Dispute Finder thus instead uses specialized approaches to identify disputed claims, and then looks for snippets that {\it entail} known disputed claims. Another advantage of this two-stage approach is that, by tying snippets to a simplified set of unique disputed claims, it becomes easier to organize articles that support and oppose a particular claim.

Dispute Finder runs a simple textual entailment algorithm inside the browser extension to detect snippets that imply disputed claims. The algorithm we use is a simple variant of the widely used Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} which is a baseline to which other algorithms are often compared~\cite{Braz}. LLM simply reduces a sentence to a bag of lemmatized words, removes stop-words, checks for negations, and then looks at what the overlap is between the words in the two phrases. Since it would not be practical for us to apply a textual entailment algorithm to all combinations of phrases on a page and disputed claims in our database, textual entailment is only attempted if a potential match is indicated by a key-phrase co-occurrence algorithm, which we discuss further in Section~\ref{our-nlp}.

\todo{Implement word weighting and word similarity?}

%Following the taxonomy used by Jijkoun and Rijke~\cite{Jijkoun2006} our algorithm is M-sim-imp, that is, we assign entailment scores based soley on word overl
%
%The algorithm we use is a simple Local Lexical Matching (LLM) algorithm.

LLM is far from being state of the art and many more sophisticated algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}. Tools such as AuContraire~\cite{Ritter2008} focus specifically on detecting contradictions. Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.

\todo{Talk about Glickman et all 2005 and MT system of Bayer et al 2005}
\todo{Cite Web Based probabalistic textual entailment}
\todo{Cite MITRE's submission to the EU PASCAL RTE Challenge}

\todo{Talk a lot about how people do textual entailment now}
\todo{Do human-guided approach that works well? Talk more about human guided task.}

\subsection{Finding Repeated Information on the Web}

\todo{is this important}

When Dispute Finder highlights many snippets that make a single disputed claim, this is a special case of the more general task of finding repeated information on the web. Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}. MemeTracker~\cite{Backstrom2009} looked for phrases shared by multiple news stories, accounting for minor variations, and used this to track the way that news flows between traditional news sources and blogs.

@@

@@

\begin{description}
\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph~\cite{Conklin1987a}. Each claim is linked to claims that represent alternative points of view, and claims that support that point of view. Each claim also has a list of articles that argue in favor of that claim (Figure\ref{popup_graph})

@@

\subsection{Argumentation Graphs}

We experimented with several different ways of explaining a disputed claim to a user. One of the approaches we implemented was a user-editable argumentation graph that connected each claim to other claims that support and oppose it, in addition to articles that argue in favor of that claim. This graph was inspired by IBIS\footnote{Issue Based Information System}~\cite{Rittel1973} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}.

Isenmann and Reuter~\cite{Isenmann1997} identified a number of problems with using IBIS tools to help people resolve disputes and make decisions. Broadly speaking, they found that opposing groups were unkeen to agree to use an IBIS tool to resolve their disputes, and that users found it difficult to properly encode a complex issue as an argument graph. We encountered similar problems with using an argumentation graph in Dispute Finder, which is why the current version of Dispute Finder presents a user with a list of articles rather than an argument graph.

@@

\todo{study result: verify}
There are significant weaknesses in this approach. Pew have shown~\cite{pew-news} that different people trust different sources. There may be little point showing liberal sources to a conservative, or vice-versa. Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments. Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.

@@

@@

Dispute Finder also provides an API that can be used by other sites to determine whether their content makes disputed claims. For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.

@@

\subsection{Web Annotation Tools}

Annotation tools such as ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content. Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips. There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}, each of which presents a different combination of features.

>>>>

The web contains a huge amount of information, but some of this information is factually incorrect~\cite{Neumann2003,Resnik1998,Zhou2004} and some sites present only one side of a contentious issue~\cite{Herman2002}. If a user is to gain a broad understanding of a topic then they will need to either spend time looking for alternative points of view, or restrict themselves to sources that they believe they can trust to provide accurate and balanced information. Even when a user spends time investigating every claim that they think might be disputed, they can still be misled by information that they had not realized was disputed.

@@

@@

Dispute Finder consists of a database, an API, and a Firefox browser extension. The database contains a set of known disputed claims that appear on the web, articles that support or oppose each disputed claim, and hints about how to determine whether a text snippet entails a known disputed claim (Figure~\ref{snippet_claim_article}). The API allows an external client to access the information in the database and use it to tell whether particular text is likely to be making a known disputed claim. The Firefox extension uses the API to determine whether the web page a user is viewing makes disputed claims. The API could also be used by other services that present users with potentially-disputed content, such as search engines, news readers, email programs, or content management systems.

In this paper, we describe the design of Dispute Finder, the trade-offs we encountered between different design choices, and our experiences testing Dispute Finder with users.

@@

Dispute Finder has been influenced by previous work in many different fields, including sensemaking, web annotation, natural language processing, and information extraction. We discuss this work throughout the paper.

\subsection{Challenges}

During the design and implementation of Dispute Finder, we had to come up with solutions for several challenges:

\begin{description}
\item[What is disputed?] To be useful, the set of known disputed claims needs to be both large and credible. If the database is too small then users will rarely see snippets highlighted. If a snippet is highlighted but there is no credible evidence for other points of view, then users will find Dispute Finder annoying. We currently crowd-source claims from users, and mine disputed claims from web sites such as Snopes and Politifact that already maintain lists of disputed claims.

\item[How do we find disputed snippets?] Given a particular web page, how do we determine which phrases on that page are making known disputed claims and should be highlighted? There is a tradeoff between precision and recall. If we highlight a snippet that is not making a disputed claim then the user will be annoyed, but if we do not highlight a snippet that is making a disputed claim then Dispute Finding missed an opportunity to be useful. We currently run a textual entailment algorithm inside the browser extension that looks for phrases that look similar to a known disputed claim.

\item[How do we highlight snippets?] If we are to alert a user when they are encountering disputed information, we need to be able to tell what information they are encountering, and be able to alert them when information they encountered was disputed. Ideally, this method should apply to as much of the information the user encounters as possible, and be easy for a user to adopt. We currently use a browser extension that checks for disputed claims on every page the user browses, and offer an API that other web sites can use to mark disputed claims on content that they serve.

\item[How should we explain a disputed claim?] Once a user has learned that a claim is disputed, it is likely that they will want to see information that will help them decide whether they should believe the claim. We currently use a simple list of articles arguing for and against the claim.

\item[What do people want?] To be useful for users, Dispute Finder needs to serve a real need that users have. We used interviews, user studies, and a small survey to try to learn what users want and what users are likely to use.
\end{description}

In the rest of this paper, we explain the various alternative solutions for each of these problems, and our experiences with the different approaches that we implemented and tested.

\subsection{Personas}

If users are going to adopt Dispute Finder, it is important that it provides users with a service that they feel will be of benefit to them, and has an interface that they can use. We designed Dispute Finder is designed to cater to two personas. Each persona was created from interviews we conducted with people who we believe fit into these categories.

@@

\section{Related Work}

Many other tools highlight disputed information on web pages. ReframeIt.com, ShiftSpace.org and SpinSpotter.com allow a user to manually annotate a web site that they disagree with, overlaying their own opinions on top of existing content. Videolyzer~\cite{Diakopoulos2008} allows users to comment on disputed claims in video clips. There are many other web annotation tools, including Google SideWiki, Annotea~\cite{Koivunen2001} and ScreenCrayons~\cite{Olsen2004}, each of which presents a different combination of features, and most of which could be used to annotate disputed content.

Several Sensemaking, Decision Support, and Argumentation tools allow a user to annotate a document with structured information that they may then share with other users. TRELLIS~\cite{Gil2002} helps a user annotate the rationale for their decisions and opinions by annotating source documents with the facts that have been extracted from them, and connecting these facts into a decision graph. ClaimSpotter~\cite{Sereno2005,Sereno2004} applies a similar approach to scholarly papers, allowing a user to make up a paper with logical subject-verb-object triples describing important claims made in the document. Entity Workspace~\cite{Bier2006} uses entity extraction algorithms to allow an intelligence analyst to easily mark up a source document with facts about it. Cohere~\cite{Shum2008} is a web based argumentation tool that allows people to connect {\it ideas} together using arbitrary verbs such as ``is an example of'', ``supports'', or ``challenges''. An idea can contain a link to a web page that contains that idea, and the Cohere Firefox Extension informs a user when the page that they are is the source for a known idea.

There are also several tools that find pages that put forward different points of view, rather than identifying disputed claims within a page. News Cube~\cite{Park2009} automatically finds articles that present different {\it aspects} of the same news story. The intention is that by reading several such aspects, the user will encounter several different ways of looking at the issue at hand, and will gained a broader perspective of the issue. 
Services such as Skewz.com and Newstrust.net allow users to rate news articles for bias. Skewz rates stories as being either liberal or conservative and encourages readers to read what the other side is thinking. Newstrust allows users to rate news articles for quality and objectivity.

On Wikipedia, WikiTrust~\cite{Adler2008a} highlights passages on Wikipedia that are statistically likely to be reverted, based on how recently they were written and the track-record of the author, Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is, and Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.

@@

If a web user trusted all the content that they read, or were unconcerned that information they read might be wrong, then it is unlikely that they they would be much demand for a service such as Dispute Finder. Fortunately, there is ample evidence that at least some people are skeptical about the information they read and would like to know about alternative points of view that are supported by sources that they trust.

According to Pew Research~\cite{PewResearch2008}, a substantial proportion of people regularly get information from sources that they do not fully trust. Their 2008 survey found that 33\% of registered democrats regularly watch Fox News, and yet only 19\% believe all or most of what Fox News says. Pew also found that online sources are viewed with more skepticism than their print, broadcast, and cable counterparts.

This result was backed up by our interviews. Several participants told us that they regularly get information from sources that they don't entirely trust. A user might read information from an untrusted source because the source is interesting, entertaining, linked to from somewhere else, or it came up in a search.

There is also evidence that a significant group of people are interested in checking information they read on the web. Several sites exist that a user can use to investigate a claim that they have read elsewhere on the web. Snopes.com contains information about urban myths such as ``eskimos have many words for snow''. Factcheck.org and Politifact.com investigate claims about US politics. According to Quantcast.com, Snopes has around five million unique visitors per month, FactCheck almost a million, and Politifact about three hundred thousand. Although these numbers are not huge compared to the really big sites, there are many other sites that people can use to check facts. In our survey, 64\% of respondents said that they often check information they read on a trusted site and 74\% of respondents said that they often check information they read by searching for other web pages with information about that topic.

Fact checking web sites and search engines work great when you know something is disputed, but are of little use if you did not realize that what you were reading was disputed. The primary aim of Dispute Finder is to let you know when something you are reading is disputed.

@@

\todo{Improve the paraphraser UI so it shows users what pages are making the claim}
\todo{Improve the ``see examples on the web'' UI to it shows the pages that were found with the activists training work}
\todo{Provide a customized RSS reader and search engine that does dispute tracking. - future work?}
\todo{Should we explicitly list what we think are our key contributions?}

\section{What is Disputed?}
\label{sec:disputed}

Dispute Finder maintains a shared database of known disputed claims. The browser extension highlights a text snippet if it believes that the snippet entails one of the claims in this database (Figure~\ref{snippet_claim_article}). Claims can either be added directly by users (Figure~\ref{add_claim}) or mined from web sites such as Snopes and Politifact that already maintain well curated databases of disputed claims,

This database should not contain contain everything that has ever been disputed by anyone. In some sense almost everything is disputed by someone on the web. There are enough people writing enough opinions that if we alerted users every time anything they read was disputed by anyone then Dispute Finder would would be so distracting as to be worthless. Similarly, there is little point spending effort rebutting claims that nobody believes. For example there is reliable evidence that the moon is made of cheese, but few people believe this claim is true. What we want is a set of claims that are widely believed and for which there is credible evidence supporting other points of view.

@@

Currently most of our claims are automatically mined Snopes and Politifact. Both of these sites maintain well curated databases of disputed claims, together with information about them. Snopes has good coverage of urban myths, and Politifact has good coverage of claims made by American Policitians. In the future we plan to crawl other sites that cover other kinds of disputed claims (e.g. medical claims) and to provide an API to allow any site to provide a well-structured feed that we can use. At the time of writing, Dispute Finder has imported 1,457 claims from Snopes and 595 claims from Politifact.

@@

An alternative approach would be to use Contradiction Detection~\cite{Ritter} to find frequently repeated statements that appear to contradict statements from trusted sources. Unfortunately at the time of writing, Contradiction Detection does not seem to be robust enough for us to use it for this purpose.

In future work, we hope to automatically find disputed claims on the web by looking for phrases like ``falsely claimed that X'' --- a similar techniques to that used by Hearst to find hyponyms~\cite{Hearst1992}.

\todo{Say how many disputed claims}
\todo{talk about duplicates}
\todo{Actually import the Politifact data}

@@

Given a web page, Dispute Finder needs to identify which snippets are making known disputed claims. Our current implementation runs a simple textual entailment algorithm inside the browser to look for sentences that entail known disputed claims.

We implemented and tested four different approaches:

@@

Explicit page marking has the highest accuracy, but the poorest coverage. Since a user is looking at the page in its entirety, they can read the snippet in context and make a good judgment about whether the snippet is indeed making the claim. However the manual effort required per page makes it difficult for this approach to scale. We also found that it can also be hard to motivate a user to mark snippets if they think that it is unlikely that another user with the Dispute Finder extension will read exactly this page. This same problem that has hindered the adoption of numerous web page annotation tools.

@@

Client side entailment gets the most coverage. Since the classification algorithm is run inside the client, the client can highlight snippets on pages that the server has not examined. This is particularly important for news pages, which are frequently read only a few minutes after they have been written. Moreover, the client-side approach can highlight snippets on web pages that would not be accessible to the server, such as web-based email, and information on an intranet.

@@

The client side entailment method uses the standard Local Lexical Matching (LLM) algorithm~\cite{Jijkoun2006} that is a common baseline to which other algorithms are often compared~\cite{Braz}. Our implementation divides the page into sentences, strips out stop-words, does stemming, and then looks for sentences that contain the keywords contained in a paraphrase of a known claim. If the claim contains a negation word (e.g. not, never, can't) then so must the matching sentence. To improve performance, rather than always running the LLM algorithm on every sentence on every page the user browses, the client starts by quickly scanning the page for ``hot terms'' such as ``Global Warming'' that are known to appear in disputed claims. The hot terms are selected such that every claim contains at least one hot term. If a hot term is found, then the sentence that contained the hot term compared against all claims about that hot term.

LLM is far from being state of the art and many more sophisticated textual entailment algorithms exist. Modern approaches include treating the sentence as a logical formula and attempting a logical proof~\cite{Bayer2001,Bos2005}, parsing each phrase into a syntax tree and using syntax heuristics~\cite{Snow2006}, infering inference rules that can transform one sentence into another while preserving meaning~\cite{Lin2002,Dinu2009,Bhagat2009}, and using baysian inference to infer whether one phrase looks like the kind of phrase that would have included each word in the other phrase~\cite{Glickman2005}. Tools such as AuContraire~\cite{Ritter} focus specifically on detecting contradictions. Several tools rely on an underlying information extraction tool such as TextRunner~\cite{Etzioni2008}.

@@

Other authors have used similar algorithms to find repeated information on the web. Kolak and Schilit~\cite{Kolak2008} look for passages places where one book quotes another, qSign~\cite{Kim2009} looks for places where one blog has quoted another, Plagiarism detectors like COPS~\cite{COPS} and SCAM~\cite{SCAM} look for places where students have copied each other, and duplicate-detection is often used to clean up web searches~\cite{web-copy-detect}. MemeTracker~\cite{Backstrom2009} looks for phrases shared by multiple news stories, accounting for minor variations, and uses this to track the way that news flows between traditional news sources and blogs.

The authors of MemeTracker observed that many ideas often flow around the web in the form of ``memes'' that are repeated on many web sites with relatively little variation. MemeTracker uses this to track the way an idea propagates across the web using a relatively simple algorithm. We have found that the precision and recall of our client-side textual entailment algorithm varies hugely depending on how meme-like a claim is. Some claims (particularly those derived from quotes) are widely repeated almost-verbatim, and can be detected relatively easily. However many other claims are rarely stated explicitly in a single sentence or with the same choice of words, making them much harder to detect with a simple algorithm.

\todo{Give an example of a good meme}

@@

When a user clicks on a highlighted snippet, Dispute Finder displays a popup interface with information intended to help the user determine whether there are alternative points of view that they should take seriously, and whether there are articles on this topic that they should read. In our current implementation, the popup interface shows lists of articles that support or oppose the claim (Figure~\ref{article_list}). We also implemented and tested an interface that contained a user-editable argumentation graph, however we found that users had difficulty creating such graphs and were more interested in {\it who} disagreed with a claim than {\it why} people disagreed with it.

@@

\begin{description}
\item[Argumentation graph:] When the user clicks on a snippet that makes a disputed claim, Dispute Finder shows them a simple user-editable argumentation graph inspired by IBIS~\footnote{Issue Based Information System} tools such as gIBIS~\cite{Conklin1987a}, Compendium~\cite{Selvin2001}, Zeno~\cite{Gordon1997}, and Cohere~\cite{Shum2008}. Each claim is linked to claims that represent alternative points of view, and claims that support that point of view. Each claim also has a list of articles that argue in favor of that claim (Figure\ref{popup_graph})

@@

@@

Unfortunately, as Pew report~\cite{PewResearch2008}, while most people say they want to receive information ``without a point of view'', the sites people actually trust tend to be those that share the person's own point of view. It seems that ``without a point of view'' is a similar concept to ``without an accent''. As a consequence, there may be little point showing liberal sources to a conservative, or vice-versa. Similarly, a global voting system can be gamed by people who vote up weak arguments against claims they support in order to hide stronger arguments. Moreover, by using moderators to decide which sources and claims are high enough quality to be presented to other users, we open ourselves up to charges of bias.

@@

Other researchers have looked at ways to determine what sources a user will trust. 
BJ Fogg et al~\cite{Fogg2003} found that the most important factor was whether a web site had a professional-looking design. Gill and Arts~\cite{Gil2006} identified on a different set of factors, including topic (a medical site may not be trusted for advice on car repair), popularity (does everyone else use this) and authority.

@@

Dispute Finder also provides an API that allows other sites to determine whether their content makes disputed claims. For example, a search engine could inform a user if its results contained disputed claims, or an RSS feed reader could tell a user if a news story makes disputed claims.

@@
